A demonstration of the \LaTeXe\ class file for \itshape{SAGE Publications}

### 2015-12-22 body/results.tex
andrea's modifications

% !TEX root =  ../main.tex
\section{Results}
\label{sec:results}
In this Section we present some of the results obtained with our planner. The complete sequences computed are shown in the companion video, TODO.
Specifically, we demonstrate the planner for two really different robots, in a large variety of environments: the humanoid HRP-2 and the quadruped HyQ~\cite{Semini}.
For each scenario we indicate the chosen heuristics. We also provide a performance analysis, which shows that the planner is compatible with interactive applications,
and present the success rates obtained in each scenario.
Moreover, we demonstrate the interest of our robustness criterion in the different computed poses.
Finally, a last example suggests possible applications to dextrous manipulation.

In our previous work~\citep{tonneauisrr15} additional results are demonstrated with various virtual avatars (Fig.~\ref{fig:robots_old}).
In this extension we choose to focus on \deleted{results obtained with} actual robots. We invite the interested reader to watch the ISRR video\endnote{https://www.youtube.com/watch?v=LmLAHgGQJGA}, and 
to refer to the previous paper for a discussion on these results.

@@

The goal is to climb three 20-cm high steps. This height requires HRP-2 to use a ramp to \deleted{be able to} perform the task.

\noindent\textbf{Contacts involved:} \deleted{Both} Feet and right arm.

\noindent\textbf{Heuristics:} The extended manipulability $h_w$ is chosen for the feet; $h_{EFORT}$ is chosen for the right arm.
Regarding equilibrium, the video demonstrates two sequences computed for two different threshold values of $b_0$: $0$ and $2$ (Fig.~\ref{fig:stair_robust}).

\noindent\textbf{Observations:}
This scenario illustrates best the importance of the equilibrium-robustness criterion.
With a robust approach, more states are required to reach the last step (15 \replaced{rather than}{against} 13 in average).
However, when the last step is reached by both feet, in the nonrobust case the contacts are extremely close to 
the cone limits\deleted{, and we believe this can be seen visually} (Fig.~\ref{fig:stair_comp}).

@@

\subsubsection{HRP-2 -- Standing up (Fig.~\ref{fig:standing}):}
From a bent configuration, a standing-up motion is computed in a cluttered environment.
The resulting motion involves using a wall as support, and climbing a 25-cm high step.

@@

\noindent\textbf{Heuristics:} $h_w$ \deleted{is used} for the feet, $h_{EFORT}$ \deleted{is used} for the hands.

\noindent\textbf{Observations:} The scenario illustrates well the acyclic aspect of the planning. For instance, in the four first frames of Fig.~\ref{fig:standing}, we can see that the right foot
is moved twice, with the left foot in between, before the configuration allows HRP-2 to move its hand.
Because the contacts are tried in a FIFO manner, the fact that the output contact sequence is acyclic shows that a cyclic approach (with a finite state machine for instance) is not sufficient
for the computed path. The reason for this is not reachability, but equilibrium. The planning is slower than for the stair scenario (because the contact generation fails more),
though it remains compatible with interactive performances. \adnote{Maybe define what you mean by 'interactive' and 'real-time' at some point.}

\subsubsection{HRP-2 -- Truck egress (Fig.~\ref{fig:TODO}):}
HRP-2 stands half seated in a truck, and \replaced{is required to}{it must} \replaced{get out}{exit} through the front window.

@@

\noindent\textbf{Heuristics:} $h_w$ \deleted{is used} for the feet, $h_{EFORT}$ \deleted{is used} for the hands.

\noindent\textbf{Observations:} This scenario demonstrates the ability of the planner to compute a path in an extremely-constrained environment. In this case,
the scenario is not always real time (TODO or is it ?): while the planner is often able to compute a guide path rapidly, in the worst case up to one minute can be spent
in the planning.

\subsubsection{HyQ -- Darpa-style rubble (Fig.~\ref{fig:darpa})}
The quadruped robot is given the task to cross a rubble composed of bricks rotated at different angles and directions.

@@

\noindent\textbf{Heuristics:} $h_w$ \deleted{is used} for all legs. The robustness threshold $b_0$ is set to $20$.

\noindent\textbf{Observations:} In this context, setting up a really important minimum value for $b_0$ is possible due to the high
stability of the HyQ robot, and results in more contact switches, in exchange for safety. The path-planning time is higher than for the previous HRP-2 robots due to the constraint that the 4 reachable workspace of all legs must
collide with the environment at all times. \adnote{Why do not relax this constraint and require only 3 legs?} Again, the computed time remains however interactive.

\subsubsection{HyQ -- Obstacle race (Figure~\ref{fig:hyq_bridge} and~\ref{fig:hyq_obs}):}
In this long scene, HyQ is first required to cross a 55-cm large hole; then, to cross a narrow "bridge",  only 25-cm large\deleted{,
while maintaining equilibrium}.

@@

\noindent\textbf{Heuristics:} $h_w$ \deleted{is used} for all legs. The robustness threshold $b_0$ is set to $4$.

\noindent\textbf{Observations:} Despite the apparent simplicity of the scene, this scenario is the hardest \deleted{to compute} for our planner.
While finding a guide path above the hole is easy for the planner, finding a \deleted{relevant} sequence of contacts that \replaced{allows for}{remain in} equilibrium is not trivial.
Second, the narrow bridge is hard both for the planner and the contact generator: to make sure that equilibrium is preserved along the traversal,
the bridge must be approached with the right angle.
This can be seen in Fig.~(TODO), where several feet \replaced{rearrangements}{repositioning} are required to cross both obstacles (although the video shows this best).
The planner however succeeds in finding a feasible sequence in the end, again with interactive computation times.

\subsubsection{HRP-2 -- Path replanning(Figure~\ref{fig:replanning}):}
In this long scene, HRP-2 plans a path through through several obstacles. the scene is edited during the execution of the motion: a stair is added,
some stepping stones are removed, and part of the final staircase is deleted. All these modifications \replaced{demands}{involve} replanning.

@@

\noindent\textbf{Contacts involved:} \replaced{F}{Both f}eet and the right arm.

\noindent\textbf{Heuristics:} $h_w$ \deleted{is used} for all legs. $h_{EFORT}$ \deleted{is used} for the right arm. The robustness threshold is set to $2$.

@@

\subsubsection{3-fingered hand -- Manipulation of a pen (Fig.~\ref{fig:penrot}):}
This scenario is proposed to illustrate the generality of our approach: we consider a manipulation task for a robotic hand and use
our contact planner to compute a guide trajectory for the fingers, considered as effectors (Fig.~\ref{fig:penrot}).
Although we do not address the hard issue of accounting for rolling motions, the planner is able to compute the shown sequences\deleted{, this} in less than 5 seconds.

@@

\noindent\textbf{Heuristics:} $h_{EFORT}$ \deleted{is used} for all fingers.

@@

\subsection{Computation times}
Table~\ref{tab:requestime} summarizes the performance measurement obtained, in terms of computation times.

@@

In most scenarios, one can observe that the average computation time for one single step is largely below the second,
thus allowing to consider interactive applications. 
Considering the repartition of the computation time, it appears that \replaced{most}{the majority} of the time is spent performing inverse kinematics.
This is not surprising considering the number of calls to the methods: IK is used intensively to maintain contact continuity between two postures; 
it is also applied every time a new candidate needs to be evaluated. However regarding state-of-the-art IK solutions, we believe there is room
for improving the performances of the algorithm.

\subsection{Success rates}
Table~\ref{tab:requestpercent} summarizes the success rates obtained for each scenario.
\begin{table*}
\centering
\begin{tabular}{ l | >{\centering\arraybackslash}m{65pt} | >{\centering\arraybackslash}m{65pt} | >{\centering\arraybackslash}m{65pt} | >{\centering\arraybackslash}m{65pt} | c}
  &  Path planning & True feasibility & Kinematic failure & Equilibrium failure \\
 \hline
   Steep stairs & 100\%  & 99.5\% & 0.11\% & 0.39\% \\
   Standing up & 100\% & 89\% & 7\% & 4\% \\
   Truck egress & \% & \% & \% &  \% \\
   Rubble & \% & \% & \% & \% \\
   Obstacle race & \% & \% & \% & \% \\
 \end{tabular}
\caption{Success rates for each scenario. The first value indicates the percentage of sucessfull complete path plannings for 1000 tests; The second value
indicates the percentage of truly feasible root configurations: considering each limb individually, indicates the percentage of root placements of the guide trajectory that
led to a feasible contact. Kinematic failure is the percentage of contact generations that failed because no collision-free candidate was found. Equilibrium failure is the percentage of contact
generations that failed because no candidate respected the static equilibrium condition.}
\label{tab:requestpercent}
\quad
\end{table*}

>>>>

% !TEX root =  ../main.tex
\section{Results}
\label{sec:results}
In this Section we present some of the results obtained with our planner. The complete sequences computed are shown in the companion video, TODO.
Specifically, we demonstrate the planner for two really different robots, in a large variety of environments: the humanoid HRP-2 and the quadruped HyQ TODO~\cite{Semini}.
For each scenario we indicate the chosen heuristics. We also provide a performance analysis, which shows that the planner is compatible with interactive applications,
and present the success rates obtained in each scenario. Moreover, we demonstrate the interest of our robustness criterion in the different computed poses.
Finally, a last example suggests possible applications to dextrous manipulation.

In our previous work~\citep{tonneauisrr15} additional results are demonstrated with various virtual avatars (Figure~\ref{fig:robots_old}).
In this extension we choose to focus on actual robots. We invite the interested reader to watch the ISRR video\endnote{https://www.youtube.com/watch?v=LmLAHgGQJGA}, and 
to refer to the previous paper for a discussion on these results.

We say that the planning is interactive when the computation time for one step is lesser than the
time to execute it. We arbitrarily approximate this time to one second.

@@

The goal is to climb three 20-cm high steps. This height requires HRP-2 to use a ramp to perform the task.

\noindent\textbf{Contacts involved:} Feet and right arm.

\noindent\textbf{Heuristics:} The extended manipulability $h_w$ is chosen for the feet; $h_{EFORT}$ is chosen for the right arm.
Regarding equilibrium, the video demonstrates two sequences computed for two different threshold values of $b_0$: $0$ and $2$ (Figure~\ref{fig:stair_robust}).

\noindent\textbf{Observations:}
This scenario illustrates best the importance of the equilibrium-robustness criterion.
With a robust approach, more states are required to reach the last step (15 rather than 13 in average).
However, when the last step is reached by both feet, in the nonrobust case the contacts are extremely close to 
the cone limits (Figure~\ref{fig:stair_comp}).

@@

\subsubsection{HRP-2 -- Standing up (Figure~\ref{fig:standing}):}
From a bent configuration, a standing-up motion is computed in a cluttered environment.
The resulting motion involves using a wall as support, and climbing a 25-cm high step.

@@

\noindent\textbf{Heuristics:} $h_w$ for the feet, $h_{EFORT}$  for the hands.

\noindent\textbf{Observations:} The scenario illustrates well the acyclic aspect of the planning. For instance, in the four first frames of Figure~\ref{fig:standing}, we can see that the right foot
is moved twice, with the left foot in between, before the configuration allows HRP-2 to move its hand.
Because the contacts are tried in a FIFO manner, the fact that the output contact sequence is acyclic shows that a cyclic approach (with a finite state machine for instance) is not sufficient
for the computed path. The reason for this is not reachability, but equilibrium. The planning is slower than for the stair scenario (because the contact generation fails more),
though it remains compatible with interactive performances. % \adnote{Maybe define what you mean by 'interactive' and 'real-time' at some point.}

%~ \subsubsection{HRP-2 -- Truck egress (Figure~\ref{fig:TODO}):}
%~ HRP-2 stands half seated in a truck, and \replaced{is required to}{it must} \replaced{get out}{exit} through the front window.

@@

%~ 
%~ \noindent\textbf{Contacts involved:} All (both feet and hands).
%~ 
%~ \noindent\textbf{Heuristics:} $h_w$ \deleted{is used} for the feet, $h_{EFORT}$ \deleted{is used} for the hands.
%~ 
%~ \noindent\textbf{Observations:} This scenario demonstrates the ability of the planner to compute a path in an extremely-constrained environment. In this case,
%~ the scenario is not always real time (TODO or is it ?): while the planner is often able to compute a guide path rapidly, in the worst case up to one minute can be spent
%~ in the planning.

\subsubsection{HyQ -- Darpa-style rubble (Figure~\ref{fig:darpa})}
The quadruped robot is given the task to cross a rubble composed of bricks rotated at different angles and directions.

@@

\noindent\textbf{Heuristics:} $h_w$ for all legs. The robustness threshold $b_0$ is set to $20$.

\noindent\textbf{Observations:} In this context, setting up a really important minimum value for $b_0$ is possible due to the high
stability of the HyQ robot, and results in more contact switches, in exchange for safety. The path-planning time is higher than for the previous HRP-2 robots due to the constraint that the 4 reachable workspace of all legs must
collide with the environment at all times. %\adnote{Why do not relax this constraint and require only 3 legs?} 
Again, the computed time remains however interactive.

\subsubsection{HyQ -- Obstacle race (Figure~\ref{fig:hyq_bridge} and~\ref{fig:hyq_obs}):}
In this long scene, HyQ is first required to cross a 55-cm large hole; then, to cross a narrow "bridge",  only 25-cm large.

@@

\noindent\textbf{Heuristics:} $h_w$ for all legs. The robustness threshold $b_0$ is set to $4$.

\noindent\textbf{Observations:} Despite the apparent simplicity of the scene, this scenario is the hardest for our planner.
While finding a guide path above the hole is easy for the planner, finding a sequence of contacts that allows for equilibrium is not trivial.
Second, the narrow bridge is hard both for the planner and the contact generator: to make sure that equilibrium is preserved along the traversal,
the bridge must be approached with the right angle.
This can is illustrated in Figure~\ref{fig:hyq_obs}, where several feet rearrangements are required to cross both obstacles (although the video shows this best).
The planner however succeeds in finding a feasible sequence in the end, again with interactive computation times.

\subsubsection{HRP-2 -- Path replanning(Figure~\ref{fig:replanning}):}
In this long scene, HRP-2 plans a path through through several obstacles. the scene is edited during the execution of the motion: a stair is added,
some stepping stones are removed, and part of the final staircase is deleted. All these modifications require replanning.

@@

\noindent\textbf{Contacts involved:} Feet and the right arm.

\noindent\textbf{Heuristics:} $h_w$  for all legs. $h_{EFORT}$  for the right arm. The robustness threshold is set to $2$.

@@

\subsubsection{3-fingered hand -- Manipulation of a pen (Figure~\ref{fig:penrot}):}
This scenario is proposed to illustrate the generality of our approach: we consider a manipulation task for a robotic hand and use
our contact planner to compute a guide trajectory for the fingers, considered as effectors (Figure~\ref{fig:penrot}).
Although we do not address the hard issue of accounting for rolling motions, the planner is able to compute the shown sequences in less than 5 seconds.

@@

\noindent\textbf{Heuristics:} $h_{EFORT}$ for all fingers.

@@

\subsubsection{Computation times}
Table~\ref{tab:requestime} summarizes the performance measurement obtained, in terms of computation times.

@@

In most scenarios, one can observe that the average computation time for one single step is largely below the second,
thus allowing to consider interactive applications. 
Considering the repartition of the computation time, it appears that most of the time is spent performing inverse kinematics.
This is not surprising considering the number of calls to the methods: IK is used intensively to maintain contact continuity between two postures; 
it is also applied every time a new candidate needs to be evaluated. However regarding state-of-the-art IK solutions, we believe there is room
for improving the performances of the algorithm.

\subsubsection{Success rates}
Table~\ref{tab:requestpercent} summarizes the success rates obtained for each scenario.
\begin{table*}
\centering
\begin{tabular}{ l | >{\centering\arraybackslash}m{65pt} | >{\centering\arraybackslash}m{65pt} | >{\centering\arraybackslash}m{65pt} | >{\centering\arraybackslash}m{65pt} | c}
  &  Path planning & True feasibility & Kinematic failure & Equilibrium failure \\
 \hline
   Steep stairs & 100\%  & 99.5\% & 0.11\% & 0.39\% \\
   Standing up & 100\% & 89\% & 7\% & 4\% \\
   Truck egress & \% & \% & \% &  \% \\
   Rubble & \% & \% & \% & \% \\
   Obstacle race & \% & \% & \% & \% \\
 \end{tabular}
\caption{Success rates for each scenario. The first value indicates the percentage of sucessfull complete path plannings for 1000 tests; The second value
indicates the percentage of truly feasible root configurations: considering each limb individually, indicates the percentage of root placements of the guide trajectory that
led to a feasible contact. Kinematic failure is the percentage of contact generations that failed because no collision-free candidate was found. Equilibrium failure is the percentage of contact
generations that failed because no candidate respected the static equilibrium condition.}
\label{tab:requestpercent}
\quad
\end{table*}
